Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase with autodiff

### 2022-11-21 src/tex/ms.tex
[showyourwork] overleaf sync

This optimisation strategy performs well, with all of the parameters being recovered down to the noise level. This can be seen in Figure~\ref{fig:data_residual} with the right panel showing a sample residual of the data and model after optimisation, which is clearly only noise. Correlations and residual plots of the positions and fluxes after the optimisation are shown in Figure~\ref{fig:astro_params}, and as expected from the residuals all of these parameters are well recovered and tightly constrained around their true values. Figure~\ref{fig:aberrations} shows the recovery of the optical aberrations, with a final residual aberration of \textcolor{red}{showyourwork variable} nm RMS. Finally, Figure~\ref{fig:flat_field} shows a correlation plot of the true and recovered sensitivity values and the corresponding residual histogram. The points of the correlation plot are colour-coded with the total counts for each pixel, showing as expected that pixels with higher photon counts having a better recovery of the PRF since these pixels have a greater \ac{snr}. Overall the parameters are very well recovered down to the noise level.

>>>>

This optimisation strategy performs well, with all of the parameters being recovered down to the noise level. This can be seen in Figure~\ref{fig:data_residual} with the right panel showing a sample residual of the data and model after optimisation, which is clearly only noise. Correlations and residual plots of the positions and fluxes after the optimisation are shown in Figure~\ref{fig:astro_params}, and as expected from the residuals all of these parameters are well recovered and tightly constrained around their true values. Figure~\ref{fig:aberrations} shows the recovery of the optical aberrations, with a final residual aberration of \variable{output/rms_opd_resid.txt} nm RMS. Finally, Figure~\ref{fig:flat_field} shows a correlation plot of the true and recovered sensitivity values and the corresponding residual histogram. The points of the correlation plot are colour-coded with the total counts for each pixel, showing as expected that pixels with higher photon counts having a better recovery of the PRF since these pixels have a greater \ac{snr}. Overall the parameters are very well recovered down to the noise level.
